Extending the WebID Protocol with Access Delegation

### 2012-08-04 paper.tex
niceup oauth section

\subsection{OAuth}
\todo{If we were to implement a secreteary like feature using OAuth what would it look like? what would the differences be?}

OAuth~2.0\footnote{http://tools.ietf.org/html/draft-ietf-oauth-v2} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant access to third-party services to their personal resources, instead of sharing their passwords with those third-party services. OAuth includes two main parts: obtaining an access token by asking the resource owner (i.e. the user) to grant access, and then using the tokens to access protected resources.

Here is a typical example of using OAuth. Ann has a Twitter account. One day she decides to support her favourite project by using Flattr\footnote{http://flattr.com/}, a micropayment service. Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr. After clicking the "Login using Twitter" button, she is redirected to Twitter's login page where she inputs her username and password. Once authenticated, Twitter informs her that Flattr.com would like to access her personal information (e.g. name, picture, etc.). She can now choose if she wants to grant or deny to Flattr access to her Twitter account information. Once she accepts, she is redirected back to Flattr.com where she notices that she is now authenticated, and her Twitter username, full name and picture now appear in Flattr.

>>>>

\subsection{OAuth}
%\todo{If we were to implement a secreteary like feature using OAuth what would it look like? what would the differences be?}

OAuth~2.0\footnote{\url{http://tools.ietf.org/html/draft-ietf-oauth-v2}} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant access to third-party services to their personal resources, instead of sharing their passwords with those third-party services.
OAuth includes two main parts: obtaining an access token by asking the resource owner (i.e. the user) to grant access, and then using the tokens to access protected resources.

Here is a typical example of using OAuth. 
Ann has a Twitter account.
One day she decides to support her favourite project by using Flattr\footnote{\url{http://flattr.com/}}, a micropayment service.
Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr.
After clicking the "Login using Twitter" button, she is redirected to Twitter's login page where she inputs her username and password.
Once authenticated, Twitter informs her that Flattr.com would like to access her personal information (e.g. name, picture, etc.).
She can now choose if she wants to grant or deny to Flattr access to her Twitter account information. Once she accepts, she is redirected back to \url{Flattr.com} where she notices that she is now authenticated, and her Twitter username, full name and picture now appear in Flattr.
